Sophize Markdown and Collaboration Interface

### 2021-07-12 paper1.tex
Cleanup
Reduce spaces, remove unnecessary code

## Hyperbola  
#oxford/T_hyperbola|EXPAND The area of a hyperbola is unbounded.

@@

\subsection*{Hyperbola}
A Hyperbola symmetrical open curve formed by the intersection of a circular cone with a plane at a smaller angle with its axis than the side of the cone. The area of a hyperbola is unbounded.

@@

The above Markdown code is rendered as:
\begin{mdframed}
Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of happiness is
what fetched \$1.3 million recently. While it may not fetch many \$s, I like the field
equations more $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
\end{mdframed}

@@

%inline the .bbl file directly for mailing to authors.

%\begin{thebibliography}{Com79}

%\bibitem[Com79]{Comer-btree}
%D.~Comer.
%\newblock The ubiquitous b-tree.
%\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.

%\bibitem[Com79]{Comer-btree}
%D.~Comer. \newblock The ubiquitous b-tree. \newblock {\em Computing Surveys}, 11(2):121--137, June 1979.

%\bibitem[Knu73]{Knuth-vol3}
%D.~E. Knuth. \newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and Searching}. \newblock Addison-Wesley, 1973.
%\end{thebibliography}

>>>>

...

@@

...

@@

Assuming the terms and propositions are referenced are available, the above Markdown code is rendered as:
\begin{mdframed}
Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of happiness is
what fetched \$1.3 million recently. While it may not fetch many \$s, I like the field
equations more $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
\end{mdframed}

@@
